---
title: "Bitcoin Analysis"
author: "Alexander J. McNeil and Martin Bladt"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bitcoin Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tscopula)
library(stats4)
library(xts)
tsoptions <- list(hessian = TRUE, method = "Nelder-Mead", avoidzero= FALSE)

```

## The Bitcoin Log-Return Data

We first load the data and calculate log-returns.

```{r, fig.show='hold', fig.width = 6, fig.height = 3, dev.args =list(pointsize=9)}
data(bitcoin)
X <- (diff(log(bitcoin))[-1]) * 100 # log-returns (as percentages)
length(X)
plot(X, type = "h")
```

## Copula Processes

### ARMA Copulas

We start with the fulcrum profile-likelihood plot which indicates that a value $\delta = 0.45$ is about right.

```{r, fig.show='hold', fig.width = 6, fig.height = 3, dev.args =list(pointsize=9)}
U <- strank(X)

copmod_Gauss <- armacopula(pars = list(ar = 0.95, ma = -0.85))
profilefulcrum(U, copmod_Gauss, locations = seq(0, 1, by = 0.05))
abline(v = 0.45)
```

We fit both the linear v-transform and the 2-parameter v-transform, starting the latter analysis close to the optimum of the first. The 2-parameter transform gives a superior fit.

```{r}
mod_Gauss <- vtscopula(copmod_Gauss, Vlinear(0.45))
fit_Gauss <- fit(mod_Gauss, U, tsoptions = tsoptions)
fit_Gauss

copmod_Gauss2 <- armacopula(pars = list(ar = 0.96, ma = -0.84))
mod_Gauss2 <- vtscopula(copmod_Gauss2, V2p(delta = 0.42))
fit_Gauss2 <- fit(mod_Gauss2, U, tsoptions = tsoptions)
fit_Gauss2
AIC(fit_Gauss, fit_Gauss2)
```

### D-Vine Copula 

Some preliminary analysis suggests that Frank copulas can work well.

```{r}
copmod <- dvinecopula(family = rep("frank", 10),
                      pars= as.list(rep(1, 10)))
mod_mix <- vtscopula(copmod, Vlinear(0.45))
tsoptions <- list(hessian = FALSE, method = "Nelder-Mead", fulcrum = 0.45)
fit_mix <- fit(mod_mix, U, tsoptions = tsoptions, control = list(maxit = 4000))
fit_mix
AIC(fit_Gauss2, fit_mix)
```

We provide plots for the model with Frank copula.

```{r, fig.show='hold', fig.width = 6, fig.height = 3, dev.args =list(pointsize=9)}
plot(fit_mix, plotoption = 1)
plot(fit_mix, plotoption = 2)
```


## Marginal Models

We fit 6 marginal distributions (3 symmetric and 3 skewed) of which the double Weibull gives the lowest AIC value.

```{r}
marg_st <- fit(margin("st"), X)
marg_sst <- fit(margin("sst"), X)
marg_lp <- fit(margin("laplace", 
                      pars = c(mu = 0.2, scale = 2.7)), X)
marg_slp <- fit(margin("slaplace", 
                pars = c(mu = 0.2, scale = 2.7, gamma = 0.9)), X)
marg_dw <- fit(margin("doubleweibull", 
                      pars = c(mu = 0.2, shape = 0.8, scale = 2.7)), X)
marg_sdw <- fit(margin("sdoubleweibull", 
                pars = c(mu = 0.2, shape = 0.8, scale = 2.7, gamma = 0.9)), X)
AIC(marg_st, marg_sst, marg_slp, marg_lp, marg_dw, marg_sdw)
```

## Full Models

We fit a full model combining the double Weibull margin with the VT-d-vine model.

```{r,fig.show='hold', dev.args =list(pointsize=9)}
fullmod <- tscm(fit_mix, margin = marg_dw)
fullmod <- fit(fullmod, as.numeric(X), 
               method = "full", tsoptions = tsoptions, control = list(maxit = 4000))
fullmod
AIC(marg_dw, fullmod)
```

The plots show aspect of the fit.

```{r,fig.show='hold', dev.args =list(pointsize=9)}
plot(fullmod, plotoption = 1)
plot(fullmod, plotoption = 2)
plot(fullmod, plottype = "margin")
plot(fullmod, plottype = "vtransform")
plot(fullmod, plottype = "volprofile")
plot(fullmod, plottype = "volproxy")
plot(fullmod, plotoption = 2, plottype = "volproxy")
```


